Keyword and Collocation analysis on India-related text of Natural History

### 2023-06-23 paper_quarto.qmd
minor fix

As mentioned earlier, the digitized text of *Natural History* with geographical annotations is readily accessible through the [TOPOSText](https://topostext.org/work/148 "Check Natural History on ToposText") project. In order to facilitate the analysis, I conducted a scraping of the full text, exporting it as a **reference corpus** in .txt format. Furthermore, I extracted the texts specifically associated with the India, utilizing the annotated coordinates, creating a **target corpus** of geographically related texts focused on India. The scraping was conducted with [Beautiful Soup](https://www.crummy.com/software/BeautifulSoup/bs4/doc/) library in Python, and the [code](https://github.com/lizaodawn/zhuang/blob/papertry/Natural%20History_corpus%20.ipynb) is uploaded to the same repository of the project.[^1]

>>>>

As mentioned earlier, the digitized text of *Natural History* with geographical annotations is readily accessible through the [TOPOSText](https://topostext.org/work/148 "Check Natural History on ToposText") project. In order to facilitate the analysis, I conducted a scraping of the full text, exporting it as a **reference corpus** in .txt format. Furthermore, I extracted the texts specifically associated with the India, utilizing the annotated coordinates, creating a **target corpus** of geographically related texts focused on India. The scraping was conducted with [Beautiful Soup](https://www.crummy.com/software/BeautifulSoup/bs4/doc/) library in Python, and the [code](https://github.com/lizaodawn/zhuang/blob/papertry/Natural%20History_corpus.ipynb) is uploaded to the same repository of the project.[^1]
